\vskip-0.6in \Large Political Uncertainty

### 2015-03-27 GS-extension.tex
solve for Vote Buyer A's simultaneous game FOC
add solution to static problem

@@

				\end{itemize}
		\end{itemize}	
	\item Vote buyer A
		\begin{itemize}
			\item Whatever we decide for vote buyer B will be the same for vote buyer A
			\item Adapting Expression~\ref{ex:objB} for Vote Buyer A
				\begin{multline}
					\max_{a(j)} \ \int_{-\frac{1}{2}}^\frac{1}{2} \left[ W_A \cdot \Phi \left(\frac{\frac{\alpha + a(j) - b(j)}{\beta} - j}{\sigma_j} \right) - b(j) \right] dj \\
						\text{subject to} \hskip.2in \int_{-\frac{1}{2}}^\frac{1}{2} a(j) dj \leq W_A  \hskip.2in \text{and} \hskip.2in a(j)\geq0 \ \forall j
							\label{ex:objA}
				\end{multline}
					\begin{itemize}
						\item Major problem if we solve this game sequentially: when substituting the FOC for Vote Buyer B (Equation~\ref{eq:focB}) into Vote Buyer A's objective function, the $a(j)$'s cancel out ($b(j)$ is linear in $a(j)$) so the benefit term is constant in $a(j)$
					\end{itemize}
		\end{itemize}
\end{enumerate}

\newpage
Comparative statics
\begin{itemize}
	\item Vote buyer B (3/25/15)
		\begin{itemize}
			\item Those for $j$, $a(j)$ and $\alpha$ don't involve the root term, so don't differ depending on whether we take the plus or minus version
				\[
					\frac{\partial b(j)}{\partial j} = -\beta \hskip.2in \frac{\partial b(j)}{\partial a(j)} = 1 \hskip.2in \frac{\partial b(j)}{\partial \alpha} = 1
				\]
			\item Those for $\beta$ and $\sigma_j$ \textit{do} involve the root term. I will only display the version for the positive root; there is also a version with all the signs reversed
				\[
				  \frac{\partial b(j)}{\partial \beta} = -j + \sigma_j \sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)} - \frac{\sigma_j}{\sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)}}
				\]
				\[
				  \frac{\partial b(j)}{\partial \sigma_j} = \beta \sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)} - \frac{\beta}{\sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)}}
				\]
		\end{itemize}
\end{itemize}

>>>>

								\label{eq:focB2}

@@

				\end{itemize}
		\end{itemize}	
	\item Vote buyer A
		\begin{itemize}
			\item Whatever we decide for vote buyer B will be the same for vote buyer A
			\item Adapting Expression~\ref{ex:objB} for Vote Buyer A
				\begin{multline}
					\max_{a(j)} \ \int_{-\frac{1}{2}}^\frac{1}{2} \left[ W_A \cdot \Phi \left(\frac{\frac{\alpha + a(j) - b(j)}{\beta} - j}{\sigma_j} \right) - a(j) \right] dj \\
						\text{subject to} \hskip.2in \int_{-\frac{1}{2}}^\frac{1}{2} a(j) dj \leq W_A  \hskip.2in \text{and} \hskip.2in a(j)\geq0 \ \forall j
							\label{ex:objA}
				\end{multline}
					\begin{itemize}
						\item Major problem if we solve this game sequentially: when substituting the FOC for Vote Buyer B (Equation~\ref{eq:focB}) into Vote Buyer A's objective function, the $a(j)$'s cancel out ($b(j)$ is linear in $a(j)$) so the benefit term is constant in $a(j)$
						\item Static best response
						  \begin{equation}
								  W_A \cdot \frac{ \partial \Phi \left(\frac{\frac{\alpha + a(j) - b(j)}{\beta} - j}{\sigma_j} \right)}{\partial a(j)} = 1
									\label{eq:focA}
							\end{equation}
						\item Math looks exactly the same as Eqn. \ref{eq:focB2} to \ref{eq:focB} except with $W_A$ replacing $W_B$ and all the opposite signs, so
							\begin{equation}
								a(j) = -\alpha + b(j)  + \beta j \pm \beta\sigma_j \sqrt{2 \left(\ln W_A - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)}
									\label{eq:focA3}
							\end{equation}		
					\end{itemize}
				\item Plugging either one of the vote buyers' FOCs into the other just implies that $W_A = W_B$, but doesn't say anything about the level of bribes. Use some kind of pareto ranking to choose one?
					\begin{itemize}
						\item Note that to get a solution, I've taken both FOCs to have the same root (either both positive or both negative; Otherwise, we need a very special combination of parameters to get an equilibrium)
						\item Intuition for this equilibrium: each vote buyer exactly brings legislator $j$ back to neutral (compensating both for inherent preference $\alpha - \beta \cdot j$) and the other vote buyer's bribe; they also each tack on a term related to WTP, $\beta$, and $\sigma_j$, but these terms cancel out as well as long as $W_A = W_B$. If $W_A \neq W_B$, then there is not such an interior equilibrium as far as I can tell. 
							\begin{itemize}
								\item Need to look for more equilibria, perhaps in mixed strategies.
								\item Especially a way to get asymmetric pure strategies (I'm happy to have asymmetry between $W_A$ and $W_B$ if necessary)
							\end{itemize}
					\end{itemize}
		\end{itemize}
\end{enumerate}

\newpage
Comparative statics
\begin{itemize}
	\item Vote buyer B (3/25/15) --- note these are not super useful yet --- they're comparative statics of the best response function, but not of the equilibrium
		\begin{itemize}
			\item Those for $j$, $a(j)$ and $\alpha$ don't involve the root term, so don't differ depending on whether we take the plus or minus version
				\[
					\frac{\partial b(j)}{\partial j} = -\beta \hskip.2in \frac{\partial b(j)}{\partial a(j)} = 1 \hskip.2in \frac{\partial b(j)}{\partial \alpha} = 1
				\]
			\item Those for $\beta$ and $\sigma_j$ \textit{do} involve the root term. I will only display the version for the positive root; there is also a version with all the signs reversed
				\[
				  \frac{\partial b(j)}{\partial \beta} = -j + \sigma_j \sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)} - \frac{\sigma_j}{\sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)}}
				\]
				\[
				  \frac{\partial b(j)}{\partial \sigma_j} = \beta \sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)} - \frac{\beta}{\sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)}}
				\]
		\end{itemize}
\end{itemize}
